Ages of Planets and Stars Observed by Kepler

### 2024-04-09 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Age distribution of stars and planet-hosts in the Kepler field
    inferred from rotation periods}.
    A histogram of samples from the age posteriors for all Kepler
    stars with reported rotation periods and temperatures is shown in
    light gray;
    the age calculation was actually valid for stars that meet the criteria
    discussed in Section~\ref{subsec:flags} (dark blue).
		\label{fig:hist_tgyro}
	}
\end{figure*}

@@

%\appendix
%\section{Can you avoid appendices?}
%\label{app:interp}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Age distribution of stars and planet-hosts in the Kepler field
    inferred from rotation periods}.
    A histogram of samples from the age posteriors for all Kepler
    stars with reported rotation periods and temperatures is shown in
    light gray;
    the age calculation was actually valid for stars that meet the criteria
    discussed in Section~\ref{subsec:flags} (dark blue).
		\label{fig:hist_tgyro}
	}
\end{figure*}

@@

\appendix
%\section{Can you avoid appendices?}
%\label{app:interp}

\section{Figure dump}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{gyroage_vs_teff_errs_showplanets_linear.png}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Gyro-age vs Teff}.
		$\pm$1$\sigma$ uncertainties are plotted around the median for Kepler stars (black) and KOIs (blue).
		Visual pileup on the left is b/c i) uncertain ages, and ii) lots of stars there.  Precision-land is the other portion.
		\label{fig:gyroage_vs_teff}
	}
\end{figure*}
